quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-04 paper-quollr.Rmd
Fixed the error with low density bins

```{r, echo=TRUE, eval=FALSE}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  benchmark_highdens = 5)
```

@@

```{r, echo=TRUE}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 10)

trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

>>>>

```{r, echo=TRUE, eval=FALSE}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  benchmark_highdens = 1)
```

@@

```{r, echo=TRUE}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 1)

trimesh <- trimesh |>
  dplyr::filter(from_count > 1,
                to_count > 1)

### 2025-08-04 paper-quollr.tex
Fixed the error with low density bins

\begin{verbatim}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  benchmark_highdens = 5)
\end{verbatim}

@@

\begin{verbatim}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 10)

trimesh <- trimesh |>
  dplyr::filter(from_count > 10,
                to_count > 10)

@@

\begin{verbatim}
> # A tibble: 5 x 4
>   pred_emb_1 pred_emb_2    ID pred_h
>        <dbl>      <dbl> <int>  <int>
> 1         NA         NA     1    215
> 2         NA         NA     2    145
> 3         NA         NA     3    116
> 4         NA         NA     4    229
> 5         NA         NA     5    229
\end{verbatim}

>>>>

\begin{verbatim}
fit_highd_model(
  highd_data = scurve, 
  nldr_data = scurve_umap, 
  b1 = 15, 
  q = 0.1, 
  benchmark_highdens = 1)
\end{verbatim}

@@

\begin{verbatim}
df_bin_centroids <- df_bin_centroids |>
  dplyr::filter(n_h > 1)

trimesh <- trimesh |>
  dplyr::filter(from_count > 1,
                to_count > 1)

@@

\begin{verbatim}
> # A tibble: 5 x 4
>   pred_emb_1 pred_emb_2    ID pred_h
>        <dbl>      <dbl> <int>  <int>
> 1      0.234      0.896     1    215
> 2      0.692      0.534     2    145
> 3      0.776      0.390     3    116
> 4      0.192      0.968     4    229
> 5      0.192      0.968     5    229
\end{verbatim}
